Tables for PM2.5 Components Paper Manuscript

### 2021-06-03 code/data-viz/correlation.Rmd
plots and tables for manuscript

dt.pmc <- dt.pmc.site.ndi %>% 
  mutate(Loc.Set = ifelse(Location.Setting == "RURAL", "Rural", "Urban"),
         Region = ifelse(Region.IV == 1, "W",
                         ifelse(Region.IV == 2, "MW",
                                ifelse(Region.IV == 3, "S", "NE")))) %>% 
    select(Site.ID, Region, Region.IV, Loc.Set) %>% 
  merge(dt.pmc)
```

```{r}
cmp.main.labels <- c("As", "Ca", "Cl", "Cu", "Fe", "K",  "Mg", "Mn", "Na", "Ni",
                     "$NO[3]^'-'", "OC", "Pb", "Se", "Si",
                     "$SO[4]^'2-'", "V", "Zn", "$PM[2.5]")
```

```{r}
corr <- dt.pmc %>%
  select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
  na.omit %>%
  cor()

@@

jpeg(here('output','plot','corr-us.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
corrplot(corr, type = "lower",  method = 'number',
         tl.col = "black", tl.srt = 45, number.cex=0.65, title = "US",mar=c(0,0,1,0),
         col = rev(brewer.pal(n = 10, name = "RdGy")))
dev.off()
```

```{r - Region}
dt.pmc<-dt.pmc[order(dt.pmc$Region.IV),] %>% 
  mutate(Region = ifelse(Region == "W", "West",
                         ifelse(Region == "MW", "Midwest",
                                ifelse(Region == "S", "South", "Northeast"))))

@@

```{r - Urbanicity}
jpeg(here('output','plot','corr-urbanicity.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
par(mfrow=c(2,2))
dt.pmc <- dt.pmc %>% arrange(Loc.Set)
for(i in unique(dt.pmc$Loc.Set)) {
  data<- subset(dt.pmc, Loc.Set==i)
  corr <- data %>%
    select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
    na.omit %>%
    cor()
  colnames(corr) <- cmp.main.labels
  rownames(corr) <- cmp.main.labels
  corrplot(corr, type = "lower",
           tl.col = "black", tl.srt = 45, number.cex=0.65, tl.cex = 0.75,
           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) 
}
dev.off()
```

>>>>

dt.pmc <- dt.pmc.site.ndi %>% 
  mutate(Loc.Set = ifelse(Location.Setting == "RURAL", "Rural", "Urban"),
         Region = ifelse(Region.IV == 1, "W",
                         ifelse(Region.IV == 2, "MW",
                                ifelse(Region.IV == 3, "S", "NE")))) %>% 
    select(Site.ID, Region, Region.IV, Loc.Set) %>% 
  merge(dt.pmc)

cmp.main.labels <- c("As", "Ca", "Cl", "Cu", "Fe", "K",  "Mg", "Mn", "Na", "Ni",
                     "$NO[3]^'-'", "OC", "Pb", "Se", "Si",
                     "$SO[4]^'2-'", "V", "Zn", "$PM[2.5]")
```

<br>

### US
```{r - US, fig.dim=c(6.5, 6.5)}
corr <- dt.pmc %>%
  select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
  na.omit %>%
  cor()

@@

jpeg(here('output','plot','corr-us.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
corrplot(corr, type = "lower",  method = 'number',
         tl.col = "black", tl.srt = 45, number.cex=0.65, tl.cex = 0.75,
         title = "US",mar=c(0,0,1,0),
         col = rev(brewer.pal(n = 10, name = "RdGy")))
dev.off()
```

<br>

### Regions
```{r - Region, fig.dim=c(6.5, 6.5)}
dt.pmc<-dt.pmc[order(dt.pmc$Region.IV),] %>% 
  mutate(Region = ifelse(Region == "W", "West",
                         ifelse(Region == "MW", "Midwest",
                                ifelse(Region == "S", "South", "Northeast"))))

@@

<br>

### Urbanicity
```{r - Urbanicity, fig.dim=c(6.5,6.5)}
jpeg(here('output','plot','corr-urbanicity.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
par(mfrow=c(2,2))
dt.pmc$Loc.Set <- as.factor(dt.pmc$Loc.Set)
dt.pmc$Loc.Set <- relevel(dt.pmc$Loc.Set, ref = "Urban")
dt.pmc <- dt.pmc %>% arrange(Loc.Set)
for(i in unique(dt.pmc$Loc.Set)) {
  data<- subset(dt.pmc, Loc.Set==i)
  corr <- data %>%
    select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
    na.omit %>%
    cor()
  colnames(corr) <- cmp.main.labels
  rownames(corr) <- cmp.main.labels
  corrplot(corr, type = "lower",
           tl.col = "black", tl.srt = 45, number.cex=0.65, tl.cex = 0.75,
           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) 
}
dev.off()
```

### 2021-06-03 code/data-viz/manuscript-tables.Rmd
plots and tables for manuscript

---
title: "Tables for PM2.5 Paper Manuscript"
author: "Fatemeh Kazemi"
date: "3/28/2021"
output:
  html_document:
    df_print: paged
---

@@

```{r load packages}
library(tidyverse)
library(here)
library(knitr)
library(kableExtra)
```

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
#load(here('output','analysis','out-fac-base-ec.RDa'))
#load(here('output','analysis','out-fac-ses-ec.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

@@

cmp.multi <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
               "Ni", "V") 
cmp.m2 <- c("PM2.5", "PM2.5", "Si", "Si", "Ca", "Ca", "Pb", "Pb", "Zn", "Zn",
            "NO3", "NO3", "OC", "OC", "Se", "Se", "SO4", "SO4", "Ni", "Ni", "V", "V")

@@

cmp.multi.res <- c("PM2.5","-Si", "-Ca", "-Pb", "-Zn", "-NO3", "-OC",
                   "-Se", "-SO4", "-Ni", "-V")

Race <- c("A", "B", "H", "W")
AgeC <- c("LE75", "M75")
```

# Figure 1a
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
    group_rows("Soil", 2, 3) %>%   # same result with group 1=
    group_rows("Metals", 4, 5) %>% 
    group_rows("Traffic", 6, 7) %>% 
    group_rows("Biomass", 8, 9) %>% 
    group_rows("Coal", 10, 11) %>%
    group_rows("Salt", 12, 13) %>% 
    group_rows("Oil", 14, 15) %>% 
    group_rows("Steel", 16, 17) %>% 
    kable_styling() %>% 
    row_spec(0, font_size = 8)
}

table_fk(data = out.pmc.ses, cmp = cmp.main, cuz = cuz.top.row)
```

# Figure 1a
```{r}
table_fk(data = out.pmc.ses, cmp = cmp.main, cuz = cuz.bot.row)
```

# Figure 1b
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

table_fk(data = out.fac.ses, cmp = So.main, cuz = cuz.top.row)
```

# Figure 1b
```{r}
table_fk(data = out.fac.ses, cmp = So.main, cuz = cuz.bot.row)
```

# Figure 2a
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    group_rows("Soil", 2, 3) %>%   # same result with group 1=
    group_rows("Metals", 4, 5) %>% 
    group_rows("Traffic", 6, 7) %>% 
    group_rows("Coal", 8, 9) %>%
    group_rows("Oil", 10, 11) %>% 
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

table_fk(data = out.pmc.resid, cmp = cmp.res, cuz = cuz.top.row)
```

# Figure 2a
```{r}
table_fk(data = out.pmc.resid, cmp = cmp.res, cuz = cuz.bot.row)
```

# Figure 2b
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

table_fk(data = out.fac.resid, cmp = So.res, cuz = cuz.top.row)
```

# Figure 2b
```{r}
table_fk(data = out.fac.resid, cmp = So.res, cuz = cuz.bot.row)
```

# Figure x
```{r}
table_fk <- function(data, cmp, cuz, em){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(!Index %in% c("Na", "Cl")) %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
    arrange(factor(Index, levels = cmp), Age),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
    group_rows("Soil", 3, 6) %>%   # same result with group 1=
    group_rows("Metals", 7, 10) %>% 
    group_rows("Traffic", 11, 14) %>% 
    group_rows("Coal", 15, 18) %>% 
    group_rows("Oil", 19, 22) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 8)
}

table_fk(data = out.pmc.age, cmp = cmp.multi, cuz = cuz.top.row)
```

```{r}
table_fk(data = out.pmc.age, cmp = cmp.multi, cuz = cuz.bot.row)
```

# Figure x2
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
    arrange(factor(Index, levels = cmp), Age),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

table_fk(data = out.fac.age, cmp = So.multi, cuz = cuz.top.row)
```

```{r}
table_fk(data = out.fac.age, cmp = So.multi, cuz = cuz.bot.row)
```

>>>>

---
title: "Tables for PM2.5 Components Paper Manuscript"
author: "Fatemeh Kazemi"
date: "05/31/2021"
output:
  html_document:
    df_print: paged
---

@@

```{r load packages}
library(tidyverse)
library(here)
library(flextable)
library(officer)
```

```{r Call Functions}
source(here('code','data-viz','manuscript-table-functions.R'))
```

```{r Load data}
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

@@

cmp.multi <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
               "Ni", "V") 
cmp.multi.labels <- c(expression("PM"[2.5]),"Si", "Ca", "Pb", "Zn", 
                      expression("NO"[3]^{"-"}), "OC", "Se", expression("SO"[4]^{"2-"}),
                      "Ni", "V")

@@

cmp.multi.res <- c("PM2.5","-Si", "-Ca", "-Pb", "-Zn", "-NO3", "-OC",
                   "-Se", "-SO4", "-Ni", "-V")
```

```{r}
doc <- read_docx()
doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.top.row,
                 cpt = "Figure 1", ftnt = "Continued ...")
doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.bot.row,
                 cpt = "Figure 1, Continued", ftnt = "")
```

```{r}
doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.top.row,
                 cpt = "Figure 2", ftnt = "Continued ...")
doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.bot.row,
                 cpt = "Figure 2, Continued", ftnt = "")
```

```{r}
doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.top.row,
                 cpt = "Figure 3", ftnt = "Continued ...")
doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.bot.row,
                 cpt = "Figure 3, Continued", ftnt = "")
```

```{r}
doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.top.row,
                 cpt = "Figure 4", ftnt = "Continued ...")
doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.bot.row,
                 cpt = "Figure 4, Continued", ftnt = "")
```

```{r}
out.pmc.race <- out.pmc.race %>% 
  mutate(Race = ifelse(Race == "A", "Asian",
                       ifelse(Race == "B", "Black",
                              ifelse(Race == "H", "Hispanic", "White"))))

doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Figure 5", ftnt = "Continued ...")
doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Figure 5, Continued", ftnt = "")
```

```{r}
out.fac.race <- out.fac.race %>% 
  mutate(Race = ifelse(Race == "A", "Asian",
                       ifelse(Race == "B", "Black",
                              ifelse(Race == "H", "Hispanic", "White"))))

doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Figure 6", ftnt = "Continued ...")
doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Figure 6, Continued", ftnt = "")
```

```{r}
out.pmc.age <- out.pmc.age %>% 
  mutate(Age = ifelse(Age == "LE75", "65-75", "> 75"),
         Age = factor(Age, levels = c("65-75", "> 75")))

doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Figure 7", ftnt = "Continued ...")
doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Figure 7, Continued", ftnt = "")
```

```{r}
out.fac.age <- out.fac.age %>% 
  mutate(Age = ifelse(Age == "LE75", "65-75", "> 75"),
         Age = factor(Age, levels = c("65-75", "> 75")))

doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Figure 8", ftnt = "Continued ...")
doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Figure 8, Continued", ftnt = "")
```

```{r}
out.pmc.sex <- out.pmc.sex %>% 
  mutate(Sex = ifelse(Sex == "F", "Female", "Male"))

doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Figure 9", ftnt = "Continued ...")
doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Figure 9, Continued", ftnt = "")
```

```{r}
out.fac.sex <- out.fac.sex %>% 
  mutate(Sex = ifelse(Sex == "F", "Female", "Male"))

doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Figure 10", ftnt = "Continued ...")
doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Figure 10, Continued", ftnt = "")
```

```{r}
doc <- Table.Single(dt = out.pmc.urbanicity %>% filter(Loc.Set == "urban") %>%
                      select(-Loc.Set),
                    cmp = cmp.main, cuz = cuz.top.row,
                 cpt = "Figure 11", ftnt = "Continued ...")
doc <- Table.Single(dt = out.pmc.urbanicity%>% filter(Loc.Set == "urban") %>% 
                      select(-Loc.Set),
                    cmp = cmp.main, cuz = cuz.bot.row,
                 cpt = "Figure 11, Continued", ftnt = "")
```

```{r}
doc <- Table.Single(dt = out.fac.urbanicity %>% filter(Loc.Set == "urban") %>% 
                      select(-Loc.Set),
                    cmp = So.main, cuz = cuz.top.row,
                 cpt = "Figure 12", ftnt = "Continued ...")
doc <- Table.Single(dt = out.fac.urbanicity%>% filter(Loc.Set == "urban") %>% 
                      select(-Loc.Set),
                    cmp = So.main, cuz = cuz.bot.row,
                 cpt = "Figure 12, Continued", ftnt = "")
```

```{r}
out.pmc.sescat <- out.pmc.sescat %>% 
  mutate(SES.Cat = ifelse(SES.Cat == "L", "Low",
                          ifelse(SES.Cat == "M", "Middle", "High")),
         SES.Cat = factor(SES.Cat, levels = c("Low", "Middle", "High")))

doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Figure 13", ftnt = "Continued ...")
doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Figure 13, Continued", ftnt = "")
```

```{r}
out.pmc.region <- out.pmc.region %>% 
  mutate(Region = ifelse(Region == "west", "West",
                         ifelse(Region == "midwest", "Midwest",
                                ifelse(Region == "south", "South", "Northeast"))),
         Region = factor(Region, levels = c("West", "Midwest", "South", "Northeast")))

doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Figure 14", ftnt = "Continued ...")
doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Figure 14, Continued", ftnt = "")
```

```{r}
out.fac.region <- out.fac.region %>% 
  mutate(Region = ifelse(Region == "west", "West",
                         ifelse(Region == "midwest", "Midwest",
                                ifelse(Region == "south", "South", "Northeast"))),
         Region = factor(Region, levels = c("West", "Midwest", "South", "Northeast")))

doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Figure 15", ftnt = "Continued ...")
doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Figure 15, Continued", ftnt = "")
```

```{r}
out.pmc.resid.region <- out.pmc.resid.region %>% 
  mutate(Region = ifelse(Region == "west", "West",
                         ifelse(Region == "midwest", "Midwest",
                                ifelse(Region == "south", "South", "Northeast"))),
         Region = factor(Region, levels = c("West", "Midwest", "South", "Northeast")))

doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.top.row,
                 cpt = "Figure 16", ftnt = "Continued ...")
doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.bot.row,
                 cpt = "Figure 16, Continued", ftnt = "")
```

```{r}
out.pmc.brfss <- out.pmc.brfss %>% 
  mutate(BRFSS = ifelse(BRFSS == "brfss0", "Base", "BRFSS-Adjusted"))

doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Figure 17", ftnt = "Continued ...")
doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Figure 17, Continued", ftnt = "")
```

```{r}
out.pmc.buffer <- out.pmc.buffer %>% 
  mutate(Buffer = ifelse(Buffer == "6", "6-miles",
                         ifelse(Buffer == "12", "12-miles", "24-miles")),
         Buffer = factor(Buffer, levels = c("6-miles", "12-miles", "24-miles")))

doc <- Table.Multi.buffer(dt = out.pmc.buffer, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Figure 18", ftnt = "Continued ...")
doc <- Table.Multi.buffer(dt = out.pmc.buffer, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Figure 18, Continued", ftnt = "")
```

```{r}
out.pmc.expo <- out.pmc.expo %>% 
  mutate(Window = ifelse(Window == "1", "1-yr",
                         ifelse(Window == "2", "2-yr",
                                ifelse(Window == "3", "3-yr",
                                       ifelse(Window == "4", "4-yr", "5-yr")))))

doc <- Table.Multi.expo(dt = out.pmc.expo, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Figure 19", ftnt = "Continued ...")
doc <- Table.Multi.expo(dt = out.pmc.expo, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Figure 19, Continued", ftnt = "")
```

```{r}
print(doc, target = here('output','table','supplement-tables.docx'))
```
